Supplement for: Carbon cycling in mature and regrowth forests globally

### 2021-02-26 manuscript/ERL_global_C_review.Rmd
working on Helene's comments
#70

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. Mean component fluxes do not necessarily add up to the mean total fluxes because different sets of sites are included depending on availability of data (Figs. S5-S30). "
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic, "The temperate conifer biome in particular is subject to high variability, with highest fluxes and stocks in the high-biomass forests of the US Pacific Northwest. An asterisk after a variable name indicates lack of C cycle closure.")  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreaal conifer forests. ", schematics_caption_generic)

@@

Data were summarized to produce schematics of C cycling for mature forests of each biome.
To obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot.
Values were then averaged across geographically distinct areas, defined as plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records.
This step was taken to avoid pseudo-replication.

We tested whether the C budgets described above "closed"--*i.e.*, whether they were internally consistent.
Specifically, we first defined relationships among variables: for example, $NEP =	GPP - R_{eco}$, $BNPP = BNPP_{coarse} + BNPP_{fine}$, $DW_{tot} = DW_{standing} + DW_{down}$).
Henceforth, we refer to the variables on the left side of the equation as "aggregate" fluxes or stocks, and those that are summed as "component" fluxes or stocks, noting that the same variable can take both aggregate and component positions in different relationships.
We considered the C budget for a given relationship "closed" when component variables summed to within one standard deviation of the aggregate variable.

To test for differences across mature forest biomes, we also examined how stand age impacted fluxes and stocks, employing a mixed effects model ['lmer' function in 'lme4' R package; @bates_fitting_2015] with biome as fixed effect and plot nested within geographic.area as random effects on the intercept.
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. 
This analysis was run for variables with records for at least seven distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1).

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand age] as fixed effects and plot nested within geographic area as a random effect on the intercept.
This analysis was run for variables with records for at least three distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1). 
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome $\times$ stand.age interaction was included in the model.
We note that the logarithmic function fit in this analysis does not always correspond to theoretical expectations (Fig. `r schematic`); however, data limitations did not support fitting of functions with more parameters or reliable comparison of different functional forms.
Within the data constraints, we deemed a logarithmic function to be the most appropriate functional form for the majority of variables.

@@

Average C cycles for mature tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major natural or anthropogenic disturbance are presented in Figures `r all_diagrams_mature` (and available in tabular format in the *ForC* release accompanying this publication:  `ForC/numbers_and_facts/ForC_variable_averages_per_Biome.csv`).

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets met our criteria for budget "closure".
That is, component variables summed to within one standard deviation of their respective aggregate variables in all but one instance.
In the temperate conifer biome, the average composite measure of root biomass ($B_{root}$) was less than the combined average value of coarse and fine root biomass ($B_{root-coarse}$ and $B_{root-fine}$, respectively).
This lack of closure was driven by very high estimates of $B_{root-coarse}$ from high-biomass forests of the US Pacific Northwest (Fig. `r B_root_coarse_fig`).

@@

There were sufficient data to assess differences among biomes in mature forest values for 15 flux variables, and significant differences among biomes were detected for 12 variables (Table 1).
In all of these cases--including C fluxes into, within, and out of the ecosystem--C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_flux_age_trends`).
Differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both.
Fluxes tended to be numerically greater in temperate broadleaf than temperate conifer forests, but the difference was never statistically significant.
This pattern held for the following variables: $GPP$, $NPP$, $ANPP$, $ANPP_{stem}$,$ANPP_{branch}$, $ANPP_{foliage}$, $BNPP$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$. 
For two of the variables without significant differences among biomes ($ANPP_{litterfall}$ and $BNPP_{fine}$; Figs. `r ANPP_litterfall_fig` and `r BNPP_fine_fig`, respectively), the same general trends applied but were not statistically significant. 
Another exception was for $BNPP_{root-coarse}$, where all records came from high-biomass forests in the US Pacific Northwest, resulting in marginally higher values for the temperate conifer biome (Fig. `r BNPP_coarse_fig`; differences significant in mixed effects model but not in post-hoc pairwise comparison).

The most notable exception to the pattern of decreasing flux per unit area from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `r NEP_fig`).
For all biomes, $NEP$ was positive, with 95% confidence intervals excluding zero.

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted line indicates the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each flux with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S5-S19).", out.width='100%', fig.pos='H'}

@@

Biome differences were less consistent across C stocks than fluxes (Figs. `r stock_age_trends`, `r all_stock_age_trends`).
There were sufficient data to assess mature forest biome differences for nine stock variables, and significant differences among biomes were detected for five variables ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$; Table 1).
For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest mean biomass and boreal forests the lowest, with intermediate means for temperate broadleaf and needleleaf forests (temperate needleleaf excluded from $B_{tot}$ analysis becuase of insufficient data; Figs. `r B_tot_fig`, `r B_ag_fig`).
However, maximum values for these variables -- along with all other  stocks including live or standing woody biomass ($B_{ag-wood}$, $B_{root}$, $B_{root-coarse}$, $DW_{tot}$, $DW_{standing}$) -- consistently occurred in temperate biomes (Figs. `r schematic`, `r stock_age_trends`, `r all_stock_age_trends`). 
For variables that were disproportionately sampled in such high-biomass forests ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$; disproportionately sampled in  the US Pacific Northwest), temperate conifer forests had significantly higher stocks than the other biomes.

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted line indicates the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each stock with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

Differences in C fluxes across biomes typically paralleled those observed for mature forests, with C cycling generally most rapid in the tropics and slowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_age_trends`).
The single exception was $ANPP_{stem}$, for which temperate broadleaf and conifer forests had flux rates similar to tropical forests.
Notably, and in contrast to the lack of biome differences in $NEP$ for mature forests (Fig. `r flux_age_trends`), the tendency for temperate forests to have greater fluxes than boreal forests held for $NEP$ in regrowth forests (tropical forests excluded because of insufficient data).

@@

*ForC* v3.0 provided unprecedented coverage of most major variables, yielding a broad picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age (Figs. `r schematic`, `r age_trends_all`).
Specifically, most C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. `r schematic`, `r flux_age_trends`- `r stock_age_trends`, `r age_trends_all`).
The notable exception was mature forest $NEP$, which, as the difference between $GPP$ and $R_{eco}$, was statistically indistinguishable across biomes (Fig. `r flux_age_trends`f).
There was also little directional variation in mean mature forest C stocks (biomass, dead wood, and organic layer) across biomes, although maximum values for the majority of stocks (all including live or standing woody biomass) occurred in temperate biomes (Figs. `r schematic`, `r all_diagrams_mature`, `r stock_age_trends`).
Consistent with theory and previous studies (Fig. `r schematic`), the majority of flux variables, together with most live biomass pools, increased significantly with stand age (Table 1; Figs. `r flux_age_trends`- `r age_trends_all`, `r all_age_trends`).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests, which are defined by the differences between in- and out- fluxes, do not vary systematically across biomes.
Together, these results refine and expand out understanding of C cycling in mature forests, while providing the first global-scale analysis of age trends in multiple forest C stocks and fluxes (Figs. `r age_trends_all`).

@@

Our analysis reveals that carbon cycling is most rapid in the tropics and slowest in boreal regions, including C fluxes into ($GPP$), within (e.g., $NPP$ and its components), and out of (e.g., $R_{soil}$, $R_{eco}$) the ecosystem.
For mature forests, this is consistent with a large body of previous work demonstrating that C fluxes generally decline with latitude -- or increase with temperature -- on a global scale [e.g., @luyssaert_co2_2007;  @gillman_latitude_2015; @li_mapping_2019; @banbury_morgan_global_nodate].
This consistency is not surprising, particularly given commonality in the data analyzed or used for calibration.
The finding that these patterns hold consistently across across numerous fluxes, while consistent with theoretical expectations (Fig. `r schematic`), is novel to this analysis [but see @banbury_morgan_global_nodate for nine autotrophic fluxes].

@@

In contrast to C fluxes and biomass accumulation rates in regrowth forests, stocks showed less systematic variation across biomes (c.f. Fig. `r schematic`).
For aboveground biomass, which is the variable in *ForC* with broadest geographical representation, the modest trend of declining biomass from tropical to boreal regions mirrors observations from spaceborne lidar that reveal a decline in aboveground biomass (for all forests, including secondary) with latitude across the N hemisphere [@hu_mapping_2016]. 
The highest- biomass forests on Earth are, however, found in coastal temperate climates of both the southern and northern hemisphere [Figs. `r schematic`, `r stock_age_trends`a; @keith_re-evaluation_2009; @smithwick_potential_2002; @hu_mapping_2016]. 
Disproportionate representation of forests in one such region--the US Pacific Northwest--inflated estimates of temperate conifer fluxes and stocks for some variables and was responsible for all of the anomalous results described here (e.g., lack of complete C budget closure, anomalous trend across biomes for $BNPP_{coarse}$). 
Thus, biome differences should always be interpreted relative to the geographic distribution of sampling, which only rarely covers the majority of forested area within a biome.

Whereas aboveground biomass can be remotely sensed [albeit with significant uncertainties; @ploton_spatial_2020] and receives significant research attention, far less is known about geographical variation in deadwood and organic layer ($OL$) across biomes, which has proved a limitation for C accounting efforts [@pan_large_2011].
Although these stocks can be important--exceeding 100 Mg C ha^-1^ in some stands (Figs. `r stock_age_trends`, `r DW_tot_fig`-`r DW_down_fig`), this study is the first to synthesize deadwood data on a global scale [but see @cook-patton_mapping_2020 for young forests].
Unfortunately, data remain too sparse for statistical comparison across biomes (Figs. `r stock_age_trends`, `r DW_tot_fig`-`r DW_down_fig`; but see below for age trends), pointing to a need for more widespread quantification of both standing and downed deadwood.
*ForC* coverage of $OL$ stocks is more comprehensive, revealing no significant differences across temperate and tropical biomes, but a tendency towards higher $OL$ in boreal forests, consistent with the idea that proportionally slower decomposition in colder climates results in more buildup of organic matter [Fig. `r schematic`; @allen_global_2002; @andersonteixeira_differential_2011]. 
Further research on non-living C stocks in the world's forests will be essential to completing the picture.

@@

Our study reveals that most C fluxes quickly increase and then decelerate as stands age (Figs. `r flux_age_trends`, `r age_trends_all`), consistent with current understanding of age trends in forest C cycling [Fig. `r schematic`; e.g., @andersonteixeira_altered_2013; @amiro_ecosystem_2010; @magnani_human_2007].
While limited records in very young (*i.e.*, <5 year old) stands resulted in poor resolution of the earliest phases of this increase for many variables (sometimes detecting no age trend; Table 1), any autotrophic C flux (e.g., $GPP$, $NPP$ and its components, $R_{auto}$) would be minimal immediately following a stand-clearing disturbance (Fig. `r schematic`).
These would be expected to increase rapidly, along with the most metabolically active components of biomass, foliage and fine roots, which also increase rapidly with stand age (Figs. `r schematic`, `r flux_age_trends`-`r age_trends_all`).
In contrast, soil heterotrophic respiration ($R_{het-soil}$) and total soil respiration ($R_{soil}$)--and therefore $R_{eco}$ are expected to be non-zero following stand-clearing disturbance (Fig. `r schematic`), although these may decrease with a reduction of root respiration ($R_{soil}$ only) and C exudates or increase in response to an influx of dead roots and litter [@ribeiro-kumara_how_2020; @maurer_carbon_2016; @bond-lamberty_contribution_2004].
In this study, we detect no significant age trends in either $R_{het-soil}$ or $R_{soil}$, consistent with previous findings [@law_changes_2003;@pregitzer_carbon_2004;@goulden_patterns_2011].

>>>>

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std over geographically distinct areas (clusters of plots within 25 km of each other). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. Mean component fluxes do not necessarily add up to the mean total fluxes because different sets of sites are included depending on availability of data (Figs. S5-S30). Mature forests are defined  as ≥ 100 years old and with no known major natural or anthropogenic disturbance in that time."
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic, "The temperate conifer biome in particular is subject to high variability, with highest fluxes and stocks in the high-biomass forests of the US Pacific Northwest. An asterisk after a variable name indicates lack of C cycle closure.")  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreaal conifer forests. ", schematics_caption_generic)

@@

We calculated means and standard deviations of each mature forest C cycle variable by biome over geographically distinct areas to produce biome-specific schematics.
We first averaged any repeated measurements within a plot.
To avoid pseudo-replication, we then averaged multiple measurements within geographically distinct areas, defined as plots clustered within 25 km of one another  [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records.
Finally, we took means and standard deviations over geographic areas.

We tested whether the C budgets described above "closed"--*i.e.*, whether they were internally consistent.
Specifically, we first defined relationships among variables: for example, $NEP =	GPP - R_{eco}$, $BNPP = BNPP_{coarse} + BNPP_{fine}$, $DW_{tot} = DW_{standing} + DW_{down}$).
Henceforth, we refer to the variables on the left side of the equation as "aggregate" fluxes or stocks, and those that are summed as "component" fluxes or stocks, noting that the same variable can take both aggregate and component positions in different relationships.
We considered the C budget for a given relationship “closed” when the means of component variables summed to within one standard deviation of the mean of the aggregate variable.

To test for differences across mature forest biomes, we also examined how stand age impacted fluxes and stocks, employing a mixed effects model ['lmer' function in 'lme4' R package; @bates_fitting_2015] with biome as fixed effect and plot nested within geographic.area as random effects on the intercept.
When biome had a significant effect, we used a Tukey's pairwise comparison to see which biomes were significantly different from one another. 
This analysis was run for variables and biomes with records for at least seven distinct geographic areas per biome (Table 1).

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand age] as fixed effects and plot nested within geographic area as a random effect on the intercept.
This analysis was run for variables and biomes with records for at least three distinct geographic areas per biome, excluding any biomes that failed this criteria (Table 1).
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome $\times$ stand.age interaction was included in the model.
We note that the logarithmic function fit in this analysis does not always correspond to theoretical expectations (Fig. `r schematic`); however, data limitations did not support fitting of functions with more parameters or reliable comparison of different functional forms.
Within the data constraints, we deemed a logarithmic function to be the most appropriate functional form for the majority of variables.

@@

Average C cycles for mature tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests are presented in Figures `r all_diagrams_mature` (and available in tabular format in the *ForC* release accompanying this publication:  `ForC/numbers_and_facts/ForC_variable_averages_per_Biome.csv`).

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets met our criteria for budget "closure".
That is, component variables summed to within one standard deviation of their respective aggregate variables in all but one instance.
In the temperate conifer biome, the average composite measure of root biomass ($B_{root}$) was less than the combined average value of coarse and fine root biomass ($B_{root-coarse}$ and $B_{root-fine}$, respectively).
This lack of closure was driven by very high estimates of $B_{root-coarse}$ from high-biomass forests of the US Pacific Northwest, a geographic region with a disproportionately large number of records for this variable (Fig. `r B_root_coarse_fig`).

@@

There were sufficient data to assess differences among biomes in mature forest values for 15 flux variables, and 12 of these variables exhibited statistically significant differences among biomes (Table 1).
In all cases of significant differences (including C fluxes into, within, and out of the ecosystem), C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_flux_age_trends`).
Differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both.
Fluxes tended to be numerically greater in temperate broadleaf than temperate conifer forests, but the difference was never statistically significant.
This pattern held for 11 of the 12 variables with significant biome effects: $GPP$, $NPP$, $ANPP$, $ANPP_{stem}$,$ANPP_{branch}$, $ANPP_{foliage}$, $BNPP$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$. 
For two of the variables without significant differences among biomes ($ANPP_{litterfall}$ and $BNPP_{fine}$; Figs. `r ANPP_litterfall_fig` and `r BNPP_fine_fig`, respectively), the same general trends applied but were not statistically significant.

The most notable exception to the pattern of decreasing flux per unit area from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `r NEP_fig`).
For all biomes, $NEP$ was positive, with 95% confidence intervals excluding zero.
$BNPP_{root-coarse}$ also exhibited significant differences among biomes with the highest means outside the tropics, in this case in temperate conifer forest, a biome for which all records came from high-biomass forests in the US Pacific Northwest (Fig. `r BNPP_coarse_fig`; differences significant in mixed effects model but not in post-hoc pairwise comparison).

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. The scatterplots show age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted lines indicate the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction (interaction effects were tested only if the main age effect was significant and data were available for at least 10 stand ages per biome--i.e., for $GPP$, $ANPP$, $R_{soil}$, and $NEP$). The boxplots illustrate variation among biomes in mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or tests of differences across biomes (mature forests, indicated by a dash instead of a letter above the box plot). Individual figures for each flux with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S5-S19).", out.width='100%', fig.pos='H'}

@@

Biome differences were less consistent across C stocks than fluxes (Figs. `r stock_age_trends`, `r all_stock_age_trends`).
There were sufficient data to assess mature forest biome differences for nine stock variables, and significant differences among biomes were detected for five variables ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$; Table 1).
For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest mean biomass and boreal forests the lowest, with intermediate means for temperate broadleaf and needleleaf forests (temperate needleleaf excluded from $B_{tot}$ analysis becuase of insufficient data; Figs. `r B_tot_fig`, `r B_ag_fig`).
However, maximum values for these variables -- along with all other  stocks including live or standing woody biomass ($B_{ag-wood}$, $B_{root}$, $B_{root-coarse}$, $DW_{tot}$, $DW_{standing}$) -- consistently occurred in temperate biomes (Figs. `r schematic`, `r stock_age_trends`, `r all_stock_age_trends`). 
For variables for which temperate conifer forest records were disproportionately from high-biomass forests in the US Pacific Northwest ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$), temperate conifer forests had significantly higher stocks than other biomes.

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) $B_{ag}$, (b) $B_{foliage}$, (c) $B_{root-fine}$, (d) $DW_{standing}$, (d) $DW_{down}$, and (d) $OL$. The scatterplots show age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted lines indicate the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction (all variables but $DW_{down}$). The boxplots illustrate variation among biomes in mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or tests of differences across biomes (mature forests, indicated by a dash instead of a letter above the box plot). Individual figures for each stock with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

Differences among biomes in regrowth forest C fluxes typically paralleled those observed for mature forests, with C cycling generally most rapid in the tropics and slowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_age_trends`).
The single exception was $ANPP_{stem}$, for which temperate broadleaf and conifer forests had flux rates similar to tropical forests.
Notably, and in contrast to the lack of biome differences in $NEP$ for mature forests (Fig. `r flux_age_trends`), the tendency for temperate forests to have greater fluxes than boreal forests held for $NEP$ in regrowth forests (tropical forests excluded because of insufficient data).

@@

*ForC* v3.0 provided unprecedented coverage of most major variables, yielding a broad picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age (Figs. `r schematic`, `r age_trends_all`).
Specifically, most C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. `r schematic`, `r flux_age_trends`- `r stock_age_trends`, `r age_trends_all`).
The notable exception was mature forest $NEP$ (the difference between $GPP$ and $R_{eco}$) which was statistically indistinguishable across biomes (Fig. `r flux_age_trends`f).
There was also little directional variation in mean mature forest C stocks (biomass, dead wood, and organic layer) across biomes, although maximum values for the majority of stocks (all including live or standing woody biomass) occurred in temperate biomes (Figs. `r schematic`, `r all_diagrams_mature`, `r stock_age_trends`).
Consistent with theory and previous studies (Fig. `r schematic`), the majority of flux variables, together with most live biomass pools, increased significantly with stand age (Table 1; Figs. `r flux_age_trends`- `r age_trends_all`, `r all_age_trends`).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests, which are defined by the differences between in- and out- fluxes, do not vary systematically across biomes.
Together, these results refine and expand out understanding of C cycling in mature forests, while providing the first global-scale analysis of age trends in multiple forest C stocks and fluxes (Figs. `r age_trends_all`).

@@

Our analysis reveals that carbon cycling is most rapid in the tropics and slowest in boreal regions.
For mature forests, this is consistent with a large body of previous work demonstrating that C fluxes generally decline with latitude and increase with temperature on a global scale [e.g., @luyssaert_co2_2007;  @gillman_latitude_2015; @li_mapping_2019; @banbury_morgan_global_nodate].
This consistency is not surprising, particularly given commonality in the data analyzed or used for calibration.
The finding that these patterns hold consistently across numerous fluxes, while consistent with theoretical expectations (Fig. `r schematic`), is novel to this analysis [but see @banbury_morgan_global_nodate for nine autotrophic fluxes].

@@

In contrast to C fluxes and biomass accumulation rates in regrowth forests, stocks showed less systematic variation across biomes (c.f. Fig. `r schematic`).
For aboveground biomass, which is the variable in *ForC* with the broadest geographical representation, the modest trend of declining biomass from tropical to boreal regions mirrors observations from spaceborne lidar that reveal a decline in aboveground biomass (for all forests, including secondary) with latitude across the N hemisphere [@hu_mapping_2016]. 
The highest-biomass forests on Earth are, however, found in coastal temperate climates of both the southern and northern hemisphere [Figs. `r schematic`, `r stock_age_trends`a; @keith_re-evaluation_2009; @smithwick_potential_2002; @hu_mapping_2016; @larjavaara_temperature_2012]. 
Disproportionate representation of forests in one such region--the US Pacific Northwest--inflated estimates of temperate conifer fluxes and stocks for some variables and was responsible for all of the anomalous results described here (e.g., lack of complete C budget closure, anomalous trend across biomes for $BNPP_{coarse}$). 
Thus, biome differences should always be interpreted relative to the geographic distribution of sampling, which only rarely adequately represents the majority of forested area within a biome.

Whereas aboveground biomass can be remotely sensed [albeit with significant uncertainties; @ploton_spatial_2020] and receives significant research attention, far less is known about geographical variation in deadwood and organic layer ($OL$) carbon across biomes, which has proved a limitation for C accounting efforts [@pan_large_2011].
Although these stocks can be important--exceeding 100 Mg C ha^-1^ in some stands (Figs. `r stock_age_trends`, `r DW_tot_fig`-`r DW_down_fig`), this study is the first to synthesize deadwood data on a global scale [but see @cook-patton_mapping_2020 for young forests].
Unfortunately, data remain too sparse for statistical comparison across biomes (Figs. `r stock_age_trends`, `r DW_tot_fig`-`r DW_down_fig`; but see below for age trends), pointing to a need for more widespread quantification of both standing and downed deadwood.
*ForC* coverage of $OL$ stocks is more comprehensive, revealing no significant differences across temperate and tropical biomes, but a tendency towards higher $OL$ in boreal forests, consistent with the idea that proportionally slower decomposition in colder climates results in more buildup of organic matter [Fig. `r schematic`; @allen_global_2002; @andersonteixeira_differential_2011]. 
Further research on non-living C stocks in the world's forests will be essential to completing the picture.

@@

Our study reveals that most autotrophic C fluxes quickly increase and then decelerate as stands age (Figs. `r flux_age_trends`, `r age_trends_all`), consistent with current understanding of age trends in forest C cycling [Fig. `r schematic`; e.g., @andersonteixeira_altered_2013; @amiro_ecosystem_2010; @magnani_human_2007].
While limited records in very young (*i.e.*, <5 year old) stands resulted in poor resolution of the earliest phases of this increase for many variables (sometimes detecting no age trend; Table 1), any autotrophic C flux (e.g., $GPP$, $NPP$ and its components, $R_{auto}$) would be minimal immediately following a stand-clearing disturbance (Fig. `r schematic`).
These would be expected to increase rapidly, along with the most metabolically active components of biomass, foliage and fine roots, which also increase rapidly with stand age (Figs. `r schematic`, `r flux_age_trends`-`r age_trends_all`).
In contrast, soil heterotrophic respiration ($R_{het-soil}$) and total soil respiration ($R_{soil}$)--and therefore $R_{eco}$ are expected to be non-zero following stand-clearing disturbance (Fig. `r schematic`), although these may decrease with a reduction of root respiration ($R_{soil}$ only) and C exudates or increase in response to an influx of dead roots and litter [@ribeiro-kumara_how_2020; @maurer_carbon_2016; @bond-lamberty_contribution_2004].
In this study, we detect no significant age trends in either $R_{het-soil}$ or $R_{soil}$, consistent with previous findings [@law_changes_2003;@pregitzer_carbon_2004;@goulden_patterns_2011].
